Summary Tables

### 2020-05-13 summary_tables_outcomes.Rmd
Add table of contents, with numbered sections

---
title: "Summary Tables"
output:
  html_document:
    toc: true
    theme: united
---

@@

## Who Hit Whom matrix (normalized to annual figures)

@@

### Who hit whom matrix {#whw}

@@

```{r whw_for_all_cs, fig.width=7, fig.height=4, echo=FALSE}

@@

  st[[cs]] <- format(td, scientific = F)

  print(kable(format(td, scientific = F), caption = paste('Who Hit Whom (WHW) for all case cities for ', cs)))

@@

## TOTAL

@@

### Change in deaths {#change_death}

@@

### Change in deaths per 100,000 {#change_death_100k}

@@

## BY PATHWAY

@@

## Change in deaths per 100,000 people by age group by scenario

### Change in deaths due to injury per 100,000 {#change_death_injury_100k}

@@

### Change in deaths due to PA per 100,000 {#change_death_PA_100k}
```{r}
pa_rates <- lapply(cities,function(x) rbind(pa_totals[[x]]/t(repmat(pop_by_age[[x]],5,1))*100000, Total=colSums(pa_totals[[x]])/rep(sum(pop_by_age[[x]]),length=5)*100000))
names(pa_rates) <- cities
round_and_print(pa_rates,"Change in deaths due to PA per 100,000 in ")

@@

### Change in deaths due to AP per 100,000 {#change_death_AP_100k}
```{r}

>>>>

---
title: "Summary Tables"
output:
  html_document:
    toc: true
    toc_depth: 5
    toc_float: true
    number_sections: true
    theme: united
---

@@

# Who Hit Whom matrix (normalized to annual figures)

@@

## Who hit whom matrix {#whw}

@@

```{r whw_for_all_cs, results = 'asis', fig.width=7, fig.height=4, echo=FALSE}

@@

  qual_name <- paste(qualified_scen_name, scen)
  st[[cs]] <- format(td, scientific = F)
  cat('####', qual_name, '\n')
  print(kable(format(td, scientific = F), caption = paste('Who Hit Whom (WHW) for all case cities for ', qual_name)))
  cat('\n')

@@

# TOTAL

@@

## Change in deaths {#change_death}

@@

## Change in deaths per 100,000 {#change_death_100k}

@@

# BY PATHWAY

@@

# Change in deaths per 100,000 people by age group by scenario

## Change in deaths due to injury per 100,000 {#change_death_injury_100k}

@@

## Change in deaths due to PA per 100,000 {#change_death_PA_100k}
```{r}
pa_rates <- lapply(cities,function(x) rbind(pa_totals[[x]]/t(repmat(pop_by_age[[x]],5,1))*100000, Total=colSums(pa_totals[[x]])/rep(sum(pop_by_age[[x]]),length=5)*100000))
names(pa_rates) <- cities
round_and_print(pa_rates,"Change in deaths due to PA per 100,000 in ")

@@

## Change in deaths due to AP per 100,000 {#change_death_AP_100k}
```{r}
